The Practical Application of MST

### 2021-02-21 article.Rmd
knit to PDF

---
title: "The Practical Application of MST"
description: |
  A practical guide to the design and development of computerised multistage tests.
author:
  - name: James Page
    affiliation: SP Educational Consulting
    affiliation_url: https://www.speduconsulting.co.uk/
date: "`r Sys.Date()`"
version: 1
output:
  html_document:
    theme: cerulean
    highlight: tango
  pdf_document:
    highlight: tango
    latex_engine: lualatex
bibliography: references.bib
output: distill::distill_article
---

>>>>

---
title: "The Practical Application of MST"
author:
- name: James Page
  affiliation: SP Educational Consulting
  affiliation_url: https://www.speduconsulting.co.uk/
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document:
    highlight: tango
    latex_engine: lualatex
  html_document:
    theme: cerulean
    highlight: tango
version: 1
description: |
  A practical guide to the design and development of computerised multistage tests.
bibliography: references.bib
---
